Supermartingales and Termination Analysis of Statistical PCF

### 2020-09-30 probabilisticProgrammingMartingales.tex
minor

\lo{TODO: Typeset Fig.~\ref{fig:adk-diagram} in vector graphics using PGF/TikZ.}

@@

\paragraph{}
If Y is in CBV order and $Y \sim_c^* X$, then $Y_{cbv} = X_{cbv}$ but also $Y_{cbv} = Y$ therefore $X_{cbv}$ is unique.
\end{proof}

>>>>

%\lo{TODO: Typeset Fig.~\ref{fig:adk-diagram} in vector graphics using PGF/TikZ.}

@@

\paragraph{}
If $Y$ is in CBV order and $Y \sim_c^* X$, then $Y_{cbv} = X_{cbv}$ but also $Y_{cbv} = Y$ therefore $X_{cbv}$ is unique.
\end{proof}
